Workload Analysis of Autonomous Driving System: Apollo, Baidu Inc.

### 2019-04-21 paper/template/paper.tex
Almost finished the introduction

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dblfloatfix}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Complete Workload Analysis of Real Autonomous Driving System: Apollo, Baidu Inc.}

@@

\begin{figure}[htb]

    \centering
    \includegraphics[width=0.5\textwidth]{images/apollo_software_architecture.png}
    \caption{Apollo Software Architecture}
    \label{}
\end{figure}

\clearpage

Autonomous driving requirements.\\
Introduction to Apollo: what is it, how is it implemented, data communication.\\
Modules that are going to be analyzed.\\
Image of apollo software architecture.\\

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dblfloatfix}
\usepackage{svg}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Workload Analysis of Autonomous Driving System: Apollo, Baidu Inc.}

@@

A schematic overview of the Apollo software architecture is presented in Figure \ref{apollo_software_architecure}.
Although the communication is data-driven, is reasonable to describe the architecture starting from sensors.
Apollo supports two Full-HD cameras with two different focal lengths, 6mm and 12mm respectively, which are polled at 20 fps.
Two types of lidars are used in Apollo: 128L and 16L. The 128L lidar is set to be the master sensor in the architecture.
GPS and IMU data are provided to the localization module in order to estimate the car's position and pose.
The perception detects obstacles present in the environment perceived from cameras and lidars and then the prediction module predicts obstacle trajectories using detections, localization estimations and trajectories chosen by the planner.
Finally, the planning module selects the best trajectory, coherent to the route requested and obstacle trajectories, containing the path and speed profile to adopt.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{images/apollo_software_architecture.png}
    \caption{Apollo Software Architecture}
    \label{apollo_software_architecure}
\end{figure*}
